---
title: "Leaflet"
author: "LJW"
date: "October 17, 2020"
output:
  html_document:
    df_print: paged
always_allow_html: yes
---

## Introduction
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!


## My First Map - Attactions in Singapore

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()

```

## Add the marker for Sentosa Island . 

*Attactions in Singapore - Sentosa*

```{r, echo=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=1.25011, lng=103.83093, 
             popup="Sentosa Island")
my_map
```

## Adding Many Markers

*Adding other attractions in Singapore*

```{r}
set.seed(999)
df <- data.frame(
  lat = c(1.25011,1.28544, 1.318707, 1.282375, 1.4043, 1.4022, 1.4029 , 1.2868 , 1.3332, 1.2893), 
  long =c(103.83093 ,103.859590, 103.706442 , 103.864273 , 103.7930 , 103.7881 , 103.7917, 103.8545, 103.7362 , 103.8631))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```


## Cluster the attractions

```{r, echo=FALSE}
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```


## Adding Icons

```{r, echo=FALSE}
sgIcon <- makeIcon(
  iconUrl = "http://img.freeflagicons.com/thumb/speech_bubble_icon/singapore/singapore_640.png", 
  iconWidth = 41*225/240 , iconHeight = 41, 
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = sgIcon)
```