---
title: "R Markdown Presentation & Plotly"
author: "LJW"
date: "10/18/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Presentation & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

Using the R built-in dataset of “presidents” to plot the quarterly approval rating for the President of the United States from the first quarter of 1945 to the last quarter of 1974.

```{r cars}

library(plotly)

summary(presidents)
```

```{r pressure, echo=FALSE}
plot_ly(x=time(presidents), y=presidents, type="bar")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
